SMT-Based Generation of Symbolic Automata \thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-11-19 2017-Xudong-SMT/ActaInformatica.tex
Acta Inf paper: - Added the discussion in the last paragraph of the conclusion re architecture styles - Moved the mention of the Coordination 2019 paper (architectures with data) to that same paragraph (otherwise not clear why mention them)

\ERIC{The original specification of the nanosatellite software, using BIP architecture patterns, was handling data in the BIP components behavior, but was not able to use data in the synchronisation between components. We have shown in \cite{BHM19:Coordination} how to overcome this limit, allowing data constraints in BIP architecture connectors, and providing an encoding of such architectures in terms of open pNets.}

@@

Naturally, our next goals after the generation of the open automata
will be to model-check logical properties, and to check equivalences
of pNets. While model-checking open automata seems easy to define,
equivalence checking is more challenging. 
In~\cite{henrio:Forte2016}, we
have already found the FH-bisimulation 
to be a suitable definition. But weak equivalences, or refinements, will
definitely be useful when comparing different pNets with
different structures. For both model-checking and bisimulation, SMT methods
will be the basis for comparing open transitions.

>>>>

\ERIC{\st{The original specification of the nanosatellite software, using BIP architecture patterns, was handling data in the BIP components behavior, but was not able to use data in the synchronisation between components. We have shown in \cite{BHM19:Coordination} how to overcome this limit, allowing data constraints in BIP architecture connectors, and providing an encoding of such architectures in terms of open pNets.}}

@@

\Simon{The results presented in this paper open a number of avenues
  for future work.}
%
Naturally, our next goals after the generation of the open automata
will be to model-check logical properties, and to check equivalences
of pNets. While model-checking open automata seems easy to define,
equivalence checking is more challenging. 
In~\cite{henrio:Forte2016}, we
have already found the FH-bisimulation 
to be a suitable definition. But weak equivalences, or refinements, will
definitely be useful when comparing different pNets with
different structures. For both model-checking and bisimulation, SMT methods
will be the basis for comparing open transitions.

\Simon{BIP architectures in this paper and in the CubETH case study \cite{CubETH-case-study} involved data in the BIP components behaviour but not in the interactions among components.  We have shown in \cite{BHM19:Coordination} how to overcome this limit, allowing data transfer in BIP architecture connectors and providing an encoding of such architectures in terms of open pNets.  To push the study of BIP architecture verification using open pNets even further, one can observe that there is a certain ``regularity'' in the structure of the composed architecture in Figure~\ref{schema:ArchFailure:BIP:Double}.  Indeed, both architectures in Figures~\ref{schema:ArchFailure:BIP} and \ref{schema:ArchFailure:BIP:Double} are instances of the same \emph{architecture style} \cite{MBBS16-diagrams} for 1 and 2 monitored processes, respectively.  The question then naturally arises of whether some version of open pNets (\eg extended to accommodate a parameterised number of sub-pNets) can be used to verify certain architectural styles without instantiating them with fixed parameter values.  Although this problem is know to be undecidable in the general case (see, \eg \cite{KKW+16-foil-concur}), it would be interesting to study the interplay of existing techniques, such as well structured transition systems \cite{WSTSE!}, with open pNet extensions.}
